miniKanren with fair search strategies

### 2019-03-29 Paper/paper.tex
more section 1

@@

If a goal that can generate planty of unwanted partial 
solutions is placed at the beginning of a \texttt{conde} expressions, it might
waste a lot computational effort. Consequently, miniKanren programmers 
sometimes need to order their \texttt{conde} clauses carefully to prevent some 
clauses absorbing unproportional computational effort. For example, when a 
relational proof checker is used as a proof generator, the eliminational rules 
should comes later.
%TODO KC: prefer an example from other literatures

%TODO KC: Should we use microKanren instead?

@@

(TODO: summarize following sections) Section 2 explains why iDFS biases toward left \texttt{conde} clauses. Section 3 is about the biDFS. Section 4 is about BFS.

\section{why iDFS put more effort computing left clauses}

@@

\begin{figure}
  \lstinputlisting{Figures/disj2.rkt}
  \caption{\texttt{disj2} and \texttt{append-inf}}
  \label{disj2-and-append-inf}
\end{figure}

>>>>

The unfairness of disjunction is not unawared. (KC: discuss existing works, 
including the monad paper and Seres's paper).

@@

@@

% TODO: summarize following sections) Section 2 explains why iDFS biases toward 
% left \texttt{conde} clauses. Section 3 is about the biDFS. Section 4 is 
% about BFS.

\section{\texttt{disj} is unfair}

The multiarity disjuction operator \texttt{disj} combine its sub-goals with 
\texttt{disj2} right associatively. \texttt{disj2} is fair in the sence that it 
allocates computational effort evenly to its two sub-goals. Unfortunately, the 
fairness of \texttt{disj2} leads to the unfairness of \texttt{disj}, because the 
first sub-goal of \texttt{disj} consumes half of all computational effort.

% below are materials.

@@

% \begin{figure}
%   \lstinputlisting{Figures/disj2.rkt}
%   \caption{\texttt{disj2} and \texttt{append-inf}}
%   \label{disj2-and-append-inf}
% \end{figure}
